---
title: "R interface to AEMET API"
author: "Sevilla R users (http://sevillarusers.wordpress.com)"
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.path = "README-")
```

[![Travis build status](https://travis-ci.org/SevillaR/aemet.svg?branch=master)](https://travis-ci.org/SevillaR/aemet)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/SevillaR/aemet?branch=master&svg=true)](https://ci.appveyor.com/project/SevillaR/aemet)


Download climatic and meteorological data from Spanish Meteorological Agency (AEMET) using their API: https://opendata.aemet.es.


## Installation

```{r eval=FALSE}
library(devtools)
install_github("SevillaR/aemet")
```

## Requirements

To be able to download data from AEMET you will need a free API key which you can get at https://opendata.aemet.es.

## Usage

```{r eval=FALSE}
library(aemet)
stations <- aemet_stations(apikey)
grazalema <- aemet_climatology_station("5911A", apikey)
```


Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
  
  